Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-03 manuscript/manuscript.tex
included gc's section

@@

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function. \gc{The exponential fitness function corresponds to
multiplicative selection across sites and so serves as the simplest
directional selection model of a trait to understand the effects of genetic
architecture on the statistics we have used in the paper.}

>>>>

Finally we used forward-in-time simulations to explore the conditions under
which temporal and convergent correlations arise. We show a subset of our
results for a model of Gaussian stabilizing selection (GSS) on a phenotype
where directional selection is induced by a sudden shift in the optimum
phenotype of varying magnitudes (Figure \ref{fig:figure-4}A).  We find that
positive temporal covariances are produced by such selection (Figure
\ref{fig:figure-4}B), and that these positive temporal covariances can compound
together to generate a large proportion of allele frequency change being due to
selection (i.e. large G) over the relatively short time periods similar to our
analyzed selection datasets span (Figure \ref{fig:figure-4}C). The magnitude of
these covariances increases with the strength of selection, i.e. the variance
in fitness, such that stronger selection generates larger proportions of allele
frequency change.  We find a similar picture of stronger convergent selection
pressures generating larger convergence correlations.

These results are often relatively insensitive to the number of loci underlying
the trait, suggesting that they may be capturing highly polygenic signals.
Indeed if only a small number of loci influence the trait, the $G(t)$
trajectories are typically much more stochastic, such that replicates do not
reliably generate temporal covariances (compare Figure \ref{fig:figure-1}B to
Supplementary Material Figure XXX).

Additionally, we explored other selection schemes. We find that the long term
dynamics of the covariances under truncation selection, which generates
substantial epistasis, are richer than we see under GSS and multiplicative
selection (Supplementary Material Figure XXX).  We also conducted simulations
of purifying selection alone (i.e. background selection) and find that this can
also generate positive temporal covariances (Figure XXX), thus it is unlikely
that all of the allele frequency change we see is the result of the novel
selection pressure the populations are exposed to, and some of this selection
may be ongoing purifying selection. Only in the case of the Longshanks
experiment, does the control line mean that we can quantify selection that is
due to the novel selection pressure.

While none of our experiments have selected the populations in divergent
directions, in our simulations we find that such selection can generate
negative convergent correlations. This suggests that selection experiments
combining multiple replicates, control lines, as well as divergent selection
pressures might be quite informative for unpacking the contribution of
particular selection pressures to genome-wide allele frequency change.

@@

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function. The exponential fitness function corresponds to multiplicative
selection across sites and so serves as the simplest directional selection
model of a trait to understand the effects of genetic architecture on the
statistics we have used in the paper.
